### 2018-03-22 Sections/quantum_algorithms.tex
minor

This approach is efficient and applies to any Hamiltonian which may be decomposed into local terms as per Eq.~(\ref{eq:Ham_sim_Ham}). However many other quantum simulation algorithms have since been described for simulating different types of quantum systems with different Hamiltonian structures \cite{bib:JLP, bib:BrennenWavelets}.

\comment{Show algorithm box}

@@

\begin{table}[!htb]
\fbox{\parbox{0.965\columnwidth}{\texttt{ 
function TDA(dataPoints):
\begin{enumerate}
	\item Implement a Grover search with set-membership oracle function,
	\begin{align}
f_\epsilon(s_k) = \left\{ \begin{matrix}
 1, & \text{if}\,\,s_k\in S_k^\epsilon \\
 0, & \text{otherwise}
\end{matrix}\right.,
\end{align}
which prepares the simplicial complex superposition state,
\begin{align}
\ket\psi_k^\epsilon = \frac{1}{\sqrt{|S_k^\epsilon|}} \sum_{s_k\in S_k^\epsilon} \ket{s_k},
\end{align}
	\item Using ancillary qubits, CNOT gates and a trace-out operation, prepare the simplicial complex uniform mixed state,
	\begin{align}
\hat\rho_k^\epsilon = \frac{1}{|S_k^\epsilon|} \sum_{s_k\in S_k^\epsilon} \ket{s_k}\bra{s_k},
\end{align}
	\item Perform quantum phase-estimation on the simplicial complex mixed state.
	\item \comment{To do - show how Betti numbers are calculated. Formulas.}
	\item Algorithm has runtime,
\begin{align}
O(n^5/\delta),
\end{align}
for accuracy $\delta$.
\item $\Box$
\end{enumerate}
\includegraphics[width=0.47\textwidth]{TDA_circuit}
}}}
\caption{Quantum topological data analysis algorithm for calculating Betti numbers.} \label{alg:TDA}
\end{table}

>>>>

This approach is efficient and applies to any Hamiltonian which may be decomposed into local terms as per Eq.~(\ref{eq:Ham_sim_Ham}). However many other quantum simulation algorithms have since been described for simulating different types of quantum systems with different Hamiltonian structures \cite{bib:JLP, bib:RohdeWavelet15}. The algorithm is summarised in Alg.~\ref{alg:ham_sim}.

\begin{table}[!htb]
\fbox{\parbox{0.965\columnwidth}{\texttt{ 
function HamiltonianSimulation($\hat{H}$, $t$, $\epsilon$):
\begin{enumerate}
	\item Hamiltonian to be simulated is of the form,
    \begin{align} \label{eq:Ham_sim_Ham}
\hat{H} = \sum_{i=1}^N \hat{H}_i	,
\end{align}
where $\hat{H}_i$ are local Hamiltonians operating on low-dimensional spaces, and $\hat{H}$ is the global Hamiltonian for the entire system.
\item For each $\hat{H}_i$ construct a quantum circuit implementing the unitary,
\begin{align}
	\hat{U}_j = e^{i\hat{H}_j\frac{t}{n}}.
\end{align}
\item The degree of discretisation, $n$, is chosen according to,
\begin{align}
n = O\left(\frac{t^2}{\epsilon}\right),
\end{align}
where $t$ is evolution time and $\epsilon$ is the accuracy.
\item Apply the circuits for simulating the local Hamiltonians according to the sequence,
\begin{align}
	\hat{U} = \left(\prod_{j=1}^N \hat{U}_j \right)^n.
\end{align}
\item The algorithm has runtime,
\begin{align}
	O\left(\frac{Nt^2}{\epsilon}\right).
\end{align}
\item $\Box$
\end{enumerate}
}}}
\caption{Quantum Hamiltonian simulation algorithm.} \label{alg:ham_sim}
\end{table}

@@

\begin{table}[!htb]
\fbox{\parbox{0.965\columnwidth}{\texttt{ 
function TDA(dataPoints):
\begin{enumerate}
	\item Implement a Grover search on the set of data-points with set-membership oracle function,
	\begin{align}
f_\epsilon(s_k) = \left\{ \begin{matrix}
 1, & \text{if}\,\,s_k\in S_k^\epsilon \\
 0, & \text{otherwise}
\end{matrix}\right.,
\end{align}
which prepares the simplicial complex superposition state,
\begin{align}
\ket\psi_k^\epsilon = \frac{1}{\sqrt{|S_k^\epsilon|}} \sum_{s_k\in S_k^\epsilon} \ket{s_k},
\end{align}
	\item Using ancillary qubits, CNOT gates and a trace-out operation, prepare the simplicial complex uniform mixed state,
	\begin{align}
\hat\rho_k^\epsilon = \frac{1}{|S_k^\epsilon|} \sum_{s_k\in S_k^\epsilon} \ket{s_k}\bra{s_k},
\end{align}
	\item Perform quantum phase-estimation on the simplicial complex mixed state.
	\item \comment{To do - show how Betti numbers are calculated. Formulas.}
	\item Algorithm has runtime,
\begin{align}
O(n^5/\delta),
\end{align}
for accuracy $\delta$.
\item $\Box$
\end{enumerate}
\includegraphics[width=0.47\textwidth]{TDA_circuit}
}}}
\caption{Quantum topological data analysis algorithm for calculating Betti numbers.} \label{alg:TDA}
\end{table}
